
Import data
```{r}
location="https://github.com/G7-PUBPOL-543/wa-school-data/raw/main/2019%20Report_DistrictTotals.csv"
schools=read.csv(location)
```

Question attempting to answer and visualize: Of WA schools that have a homeless student population, what is the frequency of homeless students in Washington state?
```{r}
summary(schools$Homeless)
```

```{r}
str(schools)
```

```{r}
length(unique(schools$DistrictName))
```

```{r}
length(unique(schools$Homeless))
```


```{r}
summary(schools$Homeless)
```
```{r}
library(ggplot2)
base=ggplot(data=schools,
            aes(x=County,y=Homeless))

base + geom_boxplot()
```
This is pretty messy and difficult to read the x-axis, needs to be cleaned up. Or I can simplify my data further.


The top 5 most populous counties in WA state are: King, Pierce, Snohomish, Spokane, and Clark
I want to create a new data frame with all of the school districts in only these Top 5 Counties

```{r}
schools[schools$County=="King"|schools$County== "Pierce"|schools$County=="Snohomish"|schools$County=="Spokane"|schools$County=="Clark",]
```

creating new variable with Top 5 Counties
```{r}
Top5Counties <- schools[schools$County=="King"|schools$County== "Pierce"|schools$County=="Snohomish"|schools$County=="Spokane"|schools$County=="Clark",]
```



```{r}
library(ggplot2)
base=ggplot(data=Top5Counties,
            aes(x=County,y=Homeless))

base + geom_bar(stat='identity')
```

```{r}
aggregate(data=Top5Counties, Homeless~County,median)
```
```{r}
aggregate(data=Top5Counties, Homeless~County,mean)
```

Previous data visual is not effective. Large outliers distort the bar graph inflating the county total, the mean or median are lost and not informative with this representation.
Going to try to make this a histogram that is flipped

```{r}
library(ggplot2)
base=ggplot(data=Top5Counties,
            aes(x=County,y=Homeless))

base + geom_boxplot()
```
```{r}
plot2=base + geom_boxplot() + labs(title = "Homeless Students per County")
```

```{r}
plot2 + coord_flip()
```

```{r}
TitleLayer = list(Title = "Homesless Students in the 12th Grade",
                   SubTi = "in the Top 5 Most Populous Counties in WA",
                   XTi = "County",
                   YTi = "Homeless Counts by School District",
                   Sou = "Source: OSPI Report Card Enrollment 2019-2020 School Year")
```


Adding title layer
```{r}
plot3=plot2+ labs(title = TitleLayer$Title,
                    subtitle = TitleLayer$SubTi,
                    x = TitleLayer$XTi,
                    y = TitleLayer$YTi,
                    caption = TitleLayer$Sou)
plot3 + coord_flip()
```


```{r}
```


```{r}
```

